Survival Analysis

### 2014-04-28 paper.Rnw
Add hypothesis test for education

% TODO test

>>>>

We may verify this casual relation by performing a log-rank test assuming $\alpha = 0.05$ and where the hypotheses are:

\[ H_0: \Lambda_{ys \leq 12} = \Lambda_{ys > 12} \]
\[ H_a: \Lambda_{ys \leq 12} \neq \Lambda_{ys > 12} \]

\scriptsize
<<bfeed-education-test, echo = FALSE>>=
survdiff(Surv(duration, delta) ~ yschool > 12, data = bfeed.short)
@
\normalsize

The $p$ value from the log-rank test is lower than our $\alpha$, which means we can reject $H_0$ that having some college education makes a difference in breastfeeding durations and support our casual conclusion that having some college education indicates longer breastfeeding durations.
